---
title: "Attendance Report: `r paste0(format(seq(Sys.Date(), length = 2, by = '-1 month')[2], '%B %Y'))`"
author: 
  name: Adam E. Sokol
date: "`r paste0(format(Sys.Date(), '%B %d, %Y'))`"

format:
  pdf:
    engine: xelatex
    keep-tex: true
    indent: false
    mainfont: "Times New Roman"
    sansfont: "Arial"
    include-in-header: 
      text: '\pagenumbering{gobble}'
knitr:
  opts_chunk:
    warning: false
    message: false

header-includes: |
  \usepackage{graphicx}
  \usepackage{titling}
  \pretitle{\begin{center}\LARGE\includegraphics[width=10cm]{Student Life Logo.png}\\[\bigskipamount]}
  \posttitle{\end{center}}
  \usepackage{booktabs}
  \usepackage{pdflscape}
  \usepackage{array}
  \usepackage{float}
  \floatplacement{table}{H}
  \usepackage{amsmath}
  \usepackage{longtable}
  \usepackage{wrapfig}
  \usepackage{colortbl}
  \usepackage{pdflscape}
  \usepackage{tabu}
  \usepackage{threeparttable}
  \usepackage{threeparttablex}
  \usepackage{titling}
  \usepackage{tabularx}
  \usepackage[normalem]{ulem}
  \usepackage{makecell}
  \usepackage{xcolor}
  \usepackage{fancyhdr}
  \usepackage{multirow}
  \usepackage{multicol}
  \usepackage{indentfirst}
  \setlength{\parindent}{20pt}
  \usepackage{geometry}
  \geometry{margin=1in}
  \usepackage{afterpage}
  \usepackage{threeparttable}
  \usepackage{hanging}
  
---

```{=tex}
\fancypagestyle{mylandscape}{
\fancyhf{} 
\fancyfoot{
\makebox[\textwidth][r]{
  \rlap{\hspace{.1cm}% Push out of margin by \footskip
    \smash{
      \raisebox{\dimexpr.5\baselineskip+\footskip+.2\textheight}{
        \rotatebox{90}{Direct questions to Adam Sokol, Director of Assessment, Department of Student Life\textemdash (803-544-1349) \thepage}}}}}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}}
```

```{=tex}
\fancypagestyle{plain}{%
\fancyhf{} % clear all header and footer fields
\fancyhead[R]{\thepage} 
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\lfoot{Direct questions to Adam Sokol, Director of Assessment, Department of Student Life\textemdash \hspace{0.5mm}  803-544-1349}}
```

\newpage

\pagestyle{plain}
\pagenumbering{arabic}

# Introduction

\noindent As part of our efforts to provide relevant, up-to-date, information in a timely manner. This report will work to update and inform offices during the semester of event attendance and other demographic information. 

<!-- Reasons Better Decisions Making -->

# Methodology

\noindent The data is collected via Garnet Gate. Two reports are generated, one for the students and another for the events. The two files are combined based on `eventID`. Then a third (3^rd^) set of data with `Department` and `Team` fields is attached. The data is run through an R process to clean and create the columns used it this report. 

The results show breakdowns for each office starting with the Russell House (RHUU) as well as each offices subgroups The Sub groups were established during the 20024-25 academic year.  

# Results

## Student Life Overall

\noindent This section examines the overall counts of students by gender, race\textbackslash ethnicity, college, class standing, transfer, and first-generation status.

```{r}
#| label: Import
#| message: false
#| warning: false
#| include: false
#| paged-print: false

pacman::p_load("tidyverse", "janitor", "lubridate","stringr","forcats", "openxlsx", "tidyr","kableExtra", "scales", "knitr")

datLink <-"C:/Users/asokol/OneDrive - University of South Carolina/StudentLife/Data/Master Lists/Events Attendees Combined AY2526 FA25 SP26 20260305.xlsx"

Clean_Event <- read.xlsx(datLink, detectDates=T, sep.names= " ") %>% 
  filter(Affiliation %in% c("STUDENT", "GRAD")) %>% 
  dplyr::mutate(
    Unit  = stringr::str_squish(Unit),
    Team  = stringr::str_squish(Team),
    Event = stringr::str_squish(Event),
    Sex = stringr::str_squish(Sex)) %>%
  rename("FirstGen"= "First-gen") %>%
  filter(Semester== "Spring 2026")

totalAttend= scales::comma(nrow(Clean_Event))
uniqueAttend= scales::comma(length(unique(Clean_Event$`Campus Email`)))
# election_Cnt= scales::comma(length(which(Clean_Event$Event=="Homecoming Voting"))) Not needed in Spring semester

nRow_dat <- nrow(Clean_Event)

#footnote1= paste("The Unknown category could be inflated due to students voting in the Homecoming elections.")

```

\noindent This section examines the overall demographic information. These numbers \textbf{exclude} faculty/staff attendees. It should be noted that Student Govenment Election data is not included in this report because the data was not available at the time of this report.

\raggedright\textsf{\textbf{\textit{Gender \& Race (Overall)}}}
```{r}
#| label: ovrllGenRaceTbl
#| echo: false
#| message: false
#| warning: false
#| paged-print: false
#| cache: true

pacman::p_load("tidyverse", "janitor", "lubridate","stringr","forcats", "openxlsx", "tidyr","kableExtra", "scales", "knitr")

ovrllGenRaceTab <- Clean_Event %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>% 
  tabyl(.,Race, Sex) %>% 
  arrange(desc(Female)) %>% 
  adorn_totals(c("row","col")) %>%
  adorn_percentages("all") %>% 
  adorn_pct_formatting(digits = 2) %>% # Format percentages to 1 decimal place
  adorn_ns(position = "front")
  
nrow_ovrllGenRace= nrow(ovrllGenRaceTab)
ncols_ovrllGenRace= ncol(ovrllGenRaceTab)
align_vec <- c("l", rep("c", ncol(ovrllGenRaceTab) - 1))

kbl(ovrllGenRaceTab, booktabs = TRUE, caption = "Unique Student Interactions by Race \\& Gender", align = align_vec) %>%
  kable_styling(latex_options = c("hold_position", "scale_down")) %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(nrow_ovrllGenRace-1, hline_after = TRUE) %>%
  row_spec(nrow_ovrllGenRace, bold = TRUE) %>%
  column_spec(ncols_ovrllGenRace, bold = TRUE) #%>% 
  #footnote(symbol= footnote1)

```

\noindent Student Life had total of `r totalAttend` interactions with `r uniqueAttend` students. Notice also that the majority of our unique interactions are with female students.  

\newpage
\raggedright\textsf{\textbf{\textit{College (Overall)}}}

\noindent Next we will examine which colleges have the most attendees at our events. 

```{r}
#| label: Overall College Table
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

pacman::p_load("tidyverse", "janitor", "lubridate","stringr","forcats", "openxlsx", "tidyr","kableExtra", "scales", "knitr")

ovrllCollegeTab_manual <- Clean_Event %>%
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  count(College, name = "Count") %>%           # numeric counts
  arrange(desc(Count)) %>%
  mutate(
    GrandTotal = sum(Count, na.rm = TRUE),
    `Percentage(%)` = round(Count / GrandTotal * 100, 2)
  ) %>%
  # add totals row
  bind_rows(
    tibble(
      College = "Total",
      Count = sum(.$Count),
      GrandTotal = NA_real_,
      `Percentage(%)` = 100
    )
  ) %>%
  select(-GrandTotal) %>%
  # formatting for display
  mutate(
    Count = comma(Count),
    `Percentage(%)` = paste0(formatC(`Percentage(%)`, format = "f", digits = 2), "%")
  )

nrows_college <- nrow(ovrllCollegeTab_manual)

align_vec_college <- c("l", rep("c", ncol(ovrllCollegeTab_manual) - 1))

kbl(ovrllCollegeTab_manual,booktabs=T,caption= "Unique Student Interactions by College", align= align_vec_college) %>%
  kable_styling(latex_options = c("hold_position","scale_down"), font_size = 10, full_width = F) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrows_college-1,hline_after = T) %>% 
  row_spec(nrows_college, bold=T) #%>% 
  #footnote(symbol= footnote1)

```

\raggedright\textsf{\textbf{\textit{Class Standing (Overall)}}}

\noindent Class Standing is determined by the number of course hours completed, and not by how many years students have completed. The table shows not only the breakdown by undergraduate class, but also provides counts for our professional colleges.

```{r}
#| label: Overall Class Standing Table
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

ovrllClssStndTab <- RPTtable_fun(Clean)
  

nrow_clssStnd <- nrow(ovrllClssStndTab)
align_vec_clssstnd <- c("l", rep("c", ncol(ovrllClssStndTab) - 1))

kbl(ovrllClssStndTab,booktabs=T, longtable=T, linesep="",caption= "Unique Student Interactions by Class Standing", align=align_vec_clssstnd) %>%
  kable_styling(latex_options = c("hold_position","scale_down"), font_size = 10) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_clssStnd-1,hline_after = T) %>% 
  row_spec(nrow_clssStnd, bold=T) #%>% 
  #footnote(symbol= footnote1)

```

The most intresting piece of information here is that the Seniors are more active than the Freshman.


\raggedright\textsf{\textbf{\textit{Cohort (Overall)}}}

\noindent Since many students begin their college carrers with some college credits through early enrollment, AP courses in High School, these students may be considered Sophmores or Juniors which can skew the `Class Standing` column in the data. Inspecting the data through the lens of what cohort they fall in with can deliver additional information.     

```{r}
#| label: OvrllChrtTbl
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

ovrllCohortTbl <- Clean_Event %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  filter(Cohort!= "Unknown") %>% 
  tabyl(`Cohort`) %>% 
  rename("Count" = n, "Percentage(%)" = percent) %>%
  filter(Cohort != "Missing") %>% 
  arrange(desc(Count)) %>%
  slice_head(n = 6) %>% 
  adorn_totals("row") %>% 
  adorn_pct_formatting(digits = 2) %>% 
  mutate(across(Count, ~ comma(.))) 
   
  
CohortYr_missing <- Clean_Event %>% 
  filter(Cohort== "Unknown") %>% 
  nrow(.) %>% 
  comma(.)
  
nrow_clssStnd <- nrow(ovrllCohortTbl)
align_vec_clssstnd <- c("l", rep("c", ncol(ovrllCohortTbl) - 1))

kbl(ovrllCohortTbl,booktabs=T, longtable = T,linesep="",caption= "Unique Student Interactions by Cohort", align=align_vec_clssstnd) %>%
  kable_styling(latex_options = c("hold_position","scale_down"), font_size = 10) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_clssStnd-1,hline_after = T) %>% 
  row_spec(nrow_clssStnd, bold=T) %>% 
  footnote(general = paste0("There are ", CohortYr_missing, " students with missing cohort data. Students with cohort years before AY2019-20 were also removed."), threeparttable= T)

```

\raggedright\textsf{\textbf{\textit{Transfer Students (Overall)}}}

```{r}
#| label: CrteTrnsfr
#| echo: false
#| message: false
#| warning: false
#| paged-print: false
#| tbl-cap: Unique Interactions by Transfer Status

ovrllTrnsfrTab <- Clean_Event %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>% 
  tabyl(Transfer) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(Count)) %>%  
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))

nrow_Trnsfr <- nrow(ovrllTrnsfrTab)
align_vec_trnsfer <- c("l", rep("c", ncol(ovrllTrnsfrTab) - 1))

kbl(ovrllTrnsfrTab, booktabs=T, align= align_vec_trnsfer) %>% 
  kable_styling(latex_options = "scale_down") %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_Trnsfr-1,hline_after = T) %>% 
  row_spec(nrow_Trnsfr, bold= T) #%>% 
  #footnote(symbol= footnote1)

```

\raggedright\textsf{\textbf{\textit{First-Generation Students (Overall)}}}

```{r}
#| label: FirstGen
#| echo: false
#| message: false
#| warning: false
#| paged-print: false
#| tbl-cap: "Unique Interactions by First-Generation Status"

ovrll1stGenTab <- Clean_Event %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  tabyl(FirstGen) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(Count)) %>%  
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))
  
nrow_FrstGen <- nrow(ovrll1stGenTab)
align_vec_trnsfer <- c("l", rep("c", ncol(ovrll1stGenTab) - 1))

kbl(ovrll1stGenTab, booktabs=T, align= align_vec_trnsfer) %>% 
  kable_styling(latex_options = "scale_down") %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_FrstGen-1,hline_after = T) %>% 
  row_spec(nrow_FrstGen, bold= T) #%>% 
  #footnote(symbol= footnote1)

```

\newpage
\raggedright\textsf{\textbf{\textit{Total Interactions by Unit (Overall)}}}
\noindent The table below shows how many total interactions occured by unit.

```{r}
#| label: ovrllUnitTab
#| echo: false
#| message: false
#| warning: false
#| paged-print: false
#| tbl-cap: Total Interactions by Unit

ovrllUnitTbl <- Clean_Event %>% 
  tabyl(Unit) %>% 
  arrange(desc(n)) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))

nrow_unit <- nrow(ovrllUnitTbl)
align_vec_unit <- c("l", rep("c", ncol(ovrllUnitTbl) - 1))

kable(ovrllUnitTbl, booktabs=TRUE, linesep = "" , align= align_vec_unit) %>% 
  kable_styling(latex_options = "hold_position") %>% 
  row_spec(0, bold= T) %>% 
  row_spec(nrow_unit-1, hline_after = T) %>% 
  row_spec(nrow_unit, bold= T) #%>% 
  #footnote(symbol= footnote1)
```

## Gamecock Entertainment (GE)

This section begins the breakdown by departments. Provides unique counts and percentages by office. Gamecock Entertainment (RHUU) is the largest host of students in the Department of Student Life. This covers a wide range of events Gamecock Entertainment and their subsidiaries, Carolina Productions, Dance Marathon, and Homecoming, Takeover Tuesday,Thursday After Dark.  

\raggedright\textsf{\textbf{\textit{Unique Interactions by Race \& Gender (Combined) (Unit: GE)}}}

```{r}
#| label: RaceGenGE
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

GenRaceTabGE <- Clean_Event %>% 
  filter(Unit=="RHUU") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  tabyl(Race, Sex) %>% 
  arrange(desc(Female)) %>% 
  adorn_totals(c("row","col")) %>%
  adorn_percentages("all") %>% 
  adorn_pct_formatting(digits = 2) %>% 
  adorn_ns(position = "front")

nrow_GE <- nrow(GenRaceTabGE)
ncol_GE <- ncol(GenRaceTabGE)
align_vec_GE <- c("l", rep("c", ncol(GenRaceTabGE) - 1))

kbl(GenRaceTabGE, booktabs = TRUE, caption = "Unique Student Interactions by Race and Gender", align = align_vec_GE) %>%
  kable_styling(latex_options = c("Hold_position", "scale_down")) %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(nrow_GE-1, hline_after = TRUE) %>%
  row_spec(nrow_GE, bold = TRUE) %>%
  column_spec(ncol_GE, bold = TRUE) #%>% 
  #footnote(symbol= footnote1)

GenRaceTabGE_cnt <- Clean_Event %>% 
  filter(Unit=="RHUU")
 
nrowUnit_GE_written <- scales::comma(nrow(GenRaceTabGE_cnt))
nrowUnit_GE_numeric <- nrow(GenRaceTabGE_cnt)

GE_pct <- paste0(format((nrowUnit_GE_numeric/nRow_dat * 100), digits=4), "%")

totalEvents_UnitTeams <- unique(Clean_Event[,c("Unit", "Team", "Event")]) %>% 
  group_by(Unit, Team) %>% 
  summarize(Count= n(), .groups = "drop") %>% 
  arrange()

TotalEvents_Unit <- unique(Clean_Event[,c("Unit", "Team", "Event")]) %>% 
  group_by(Unit) %>% 
  summarize(Count=n())

numGE_events <- TotalEvents_Unit %>% 
  dplyr::filter(Unit== "RHUU") %>% 
  dplyr::pull(Count)
```

Gamecock Entertainment as a whole accounted for `{r} nrowUnit_GE_written` total student interactions making up `{r} GE_pct` of the total student engagements, hosting `{r} numGE_events` events. These tables show theat the majority of attendees are White Females. 

\newpage
\raggedright\textsf{\textbf{\textit{Unique Interactions by College (Unit: GE)}}}

```{r}
#| label: CollegeTabGE
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

CollegeTabGE <- Clean_Event %>% 
  filter(Unit == "RHUU") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>% 
  tabyl(College) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(Count)) %>%  
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))
  
nrows_collegeGE <- nrow(CollegeTabGE)

align_vec_collegeGE <- c("l", rep("c", ncol(CollegeTabGE) - 1))

kbl(CollegeTabGE,booktabs=T, caption= "Unique Student Interactions by College", align= align_vec_collegeGE) %>%
  kable_styling(latex_options = c("hold_position","scale_down"), font_size = 10) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrows_collegeGE-1,hline_after = T) %>% 
  row_spec(nrows_collegeGE, bold=T) #%>% 
  #footnote(symbol= footnote1)

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by Class Standing (Unit: GE)}}}

```{r}
#| label: ClssStndUtGE
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

pacman::p_load("tidyverse", "janitor", "lubridate","stringr","forcats", "openxlsx", "tidyr","kableExtra", "scales", "knitr")

ovrllClssStndTabGE <- Clean_Event %>% 
  filter(Unit=="RHUU") %>%
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  tabyl(`Class Standing`) %>% 
  rename("Count"= n, "Percentage(%)"=percent,) %>%
  arrange(desc(`Percentage(%)`)) %>% 
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.))) 

nrow_clssStnd <- nrow(ovrllClssStndTabGE)
align_vec_clssstnd <- c("l", rep("c", ncol(ovrllClssStndTabGE) - 1))

kbl(ovrllClssStndTabGE,booktabs=T, linesep = "", caption= "Unique Student Interactions by Class Standing", align=align_vec_clssstnd, ) %>%
  kable_styling(latex_options = c("hold_position","scale_down"), font_size = 10) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_clssStnd-1,hline_after = T) %>% 
  row_spec(nrow_clssStnd, bold=T) #%>% 
  #footnote(symbol= footnote1)
```

\newpage
\raggedright\textsf{\textbf{\textit{Unique Interactions by Cohort (Unit: GE)}}}

```{r}
#| label: ChrtTblGE
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

CohortTblGE <- Clean_Event %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  filter(Unit== "RHUU",Cohort!= "Unknown") %>% 
  tabyl(`Cohort`) %>% 
  rename("Count" = n, "Percentage(%)" = percent) %>%
  filter(Cohort != "Missing") %>% 
  arrange(desc(Count)) %>%
  slice_head(n = 6) %>% 
  adorn_totals("row") %>% 
  adorn_pct_formatting(digits = 2) %>% 
  mutate(across(Count, ~ comma(.))) 
   
CohortYr_missing <- Clean_Event %>% 
  filter(Unit== "RHUU", Cohort== "Unknown") %>% 
  nrow(.) %>% 
  comma(.)
  
nrow_clssStnd <- nrow(CohortTblGE)
align_vec_clssstnd <- c("l", rep("c", ncol(CohortTblGE) - 1))

kbl(CohortTblGE, booktabs=T, linesep="",caption= "Unique Student Interactions by Cohort", align=align_vec_clssstnd) %>%
  kable_styling(latex_options = "hold_position", font_size = 10) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_clssStnd-1,hline_after = T) %>% 
  row_spec(nrow_clssStnd, bold=T) %>% 
  footnote(general = paste0("There are ", CohortYr_missing, " students with missing cohort data. Students with cohort years before AY2019-20 were also removed."), threeparttable = TRUE)

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by Transfer (Unit: GE)}}}

```{r}
#| label: CrteTrnsfrGE
#| echo: false
#| message: false
#| warning: false
#| paged-print: false
#| tbl-cap: Unique Interactions by Transfer Status

  TrnsfrTabGE <- Clean_Event %>% 
  filter(Unit== "RHUU") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>% 
  tabyl(Transfer) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(Count)) %>%  
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))

nrow_trnsfr <- nrow(TrnsfrTabGE)
align_vec_trnsfr <- c("l", rep("c", ncol(TrnsfrTabGE) - 1))

kbl(TrnsfrTabGE, booktabs=T, align= align_vec_trnsfr) %>% 
  kable_styling(latex_options = "scale_down", full_width= F) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_trnsfr-1,hline_after = T) %>% 
  row_spec(nrow_trnsfr, bold= T) #%>% 
  #footnote(symbol= footnote1)

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by First-Gen Status (Unit: GE)}}}

```{r}
#| label: FirstGenGE
#| echo: false
#| message: false
#| warning: false
#| paged-print: false
#| tbl-cap: "Unique Interactions by First-Generation Status"

  GE1stGenTab <- Clean_Event %>% 
  filter(Unit== "RHUU") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  rename("FirstGen"= "First-gen") %>% 
  tabyl(FirstGen) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(Count)) %>%  
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))

nrow_FrstGen <- nrow(GE1stGenTab)
align_vec_trnsfer <- c("l", rep("c", ncol(GE1stGenTab) - 1))

kbl(GE1stGenTab, booktabs=T, align= align_vec_trnsfer) %>% 
  kable_styling(latex_options = "scale_down", full_width= F) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_FrstGen-1,hline_after = T) %>% 
  row_spec(nrow_FrstGen, bold= T) #%>% 
  #footnote(symbol= footnote1)

```

\newpage
### Carolina Productions (CP)

\raggedright\textsf{\textbf{\textit{Unique Interactions by Race \& Gender (Combined) (Team: CP)}}}

```{r}
#| label: RaceGenCP
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

GenRaceTabCP <- Clean_Event %>% 
  filter(Team=="Carolina Productions") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  tabyl(Race, Sex) %>% 
  arrange(desc(Female)) %>% 
  adorn_totals(c("row","col")) %>%
  adorn_percentages("all") %>% 
  adorn_pct_formatting(digits = 2) %>% 
  adorn_ns(position = "front")

nrow_CP <- nrow(GenRaceTabCP)
ncol_CP <- ncol(GenRaceTabCP)
align_vec_CP <- c("l", rep("c", ncol(GenRaceTabCP) - 1))

kbl(GenRaceTabCP, booktabs = TRUE, caption = "Unique Student Interactions by Race and Gender (Team: Carolina Productions)", align = align_vec_CP) %>%
  kable_styling(latex_options = c("Hold_position", "scale_down")) %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(nrow_CP-1, hline_after = TRUE) %>%
  row_spec(nrow_CP, bold = TRUE) %>%
  column_spec(ncol_CP, bold = TRUE) #%>% 
  #footnote(symbol= footnote1)

GenRaceTabCP_cnt <- Clean_Event %>% 
  filter(Team=="Carolina Productions")
 
nrowUnit_CP_written <- scales::comma(nrow(GenRaceTabCP_cnt))
nrowUnit_CP_numeric <- nrow(GenRaceTabCP_cnt)

CP_pct <- paste0(format((nrowUnit_CP_numeric/nRow_dat * 100), digits=4), "%")

num_duplicate_addressesCP <- Clean_Event %>%
  filter(str_detect(Team, "Carolina Productions")) %>%
  count(`Campus Email`) %>%
  filter(n > 1) %>%
  nrow()

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by College (Team: CP)}}}

```{r}
#| label: CollegeTabCP
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

CollegeTabCP <- Clean_Event %>% 
  filter(Team == "Carolina Productions") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>% 
  tabyl(College) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(Count)) %>%  
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.))) 
  

nrows_collegeCP <- nrow(CollegeTabCP)

align_vec_collegeCP <- c("l", rep("c", ncol(CollegeTabCP) - 1))

kbl(CollegeTabCP,booktabs=T, longtable = T, caption= "Unique Student Interactions by College (Team: Carolina Productions)", align= align_vec_collegeCP) %>%
  kable_styling(latex_options = c("hold_position","scale_down"), font_size = 10) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrows_collegeCP-1,hline_after = T) %>% 
  row_spec(nrows_collegeCP, bold=T) #%>% 
  #footnote(symbol= footnote1)

```

\newpage
\raggedright\textsf{\textbf{\textit{Unique Interactions by Class Standing (Team: CP)}}}
```{r}
#| label: ClssStnd_CP
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

pacman::p_load("tidyverse", "janitor", "lubridate","stringr","forcats", "openxlsx", "tidyr","kableExtra", "scales", "knitr")

ClssStndTabCP <- Clean_Event %>% 
  filter(Team=="Carolina Productions") %>%
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  tabyl(`Class Standing`) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(`Percentage(%)`)) %>% 
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2)
  
nrow_clssStnd <- nrow(ClssStndTabCP)
align_vec_clssstnd <- c("l", rep("c", ncol(ClssStndTabCP) - 1))

kbl(ClssStndTabCP,booktabs=T, linesep = "", caption= "Unique Student Interactions by Class Standing (Team: Carolina Productions)", align=align_vec_clssstnd) %>%
  kable_styling(latex_options = c("hold_position","scale_down"), font_size = 10) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_clssStnd-1,hline_after = T) %>% 
  row_spec(nrow_clssStnd, bold=T) #%>% 
  #footnote(symbol= footnote1)

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by Cohort (Unit: CP)}}}
```{r}
#| label: ChrtTblCP
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

CohortTblCP <- Clean_Event %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  filter(Team== "Carolina Productions",Cohort!= "Unknown") %>% 
  tabyl(`Cohort`) %>% 
  rename("Count" = n, "Percentage(%)" = percent) %>%
  filter( Cohort != "Missing") %>% 
  arrange(desc(Count)) %>%
  slice_head(n = 6) %>% 
  adorn_totals("row") %>% 
  adorn_pct_formatting(digits = 2) %>% 
  mutate(across(Count, ~ comma(.))) 
   
  
CohortYr_missing <- Clean_Event %>% 
  filter(Team== "Carolina Productions",Cohort== "Unknown") %>% 
  nrow(.) %>% 
  comma(.)
  
nrow_clssStnd <- nrow(ovrllCohortTbl)
align_vec_clssstnd <- c("l", rep("c", ncol(ovrllCohortTbl) - 1))

kbl(CohortTblCP,booktabs=T, linesep="",caption= "Unique Student Interactions by Cohort", align=align_vec_clssstnd) %>%
  kable_styling(latex_options = c("hold_position","scale_down"), font_size = 10) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_clssStnd-1,hline_after = T) %>% 
  row_spec(nrow_clssStnd, bold=T) %>% 
  footnote(general = "Students with cohort years before AY2019-20 were removed.", threeparttable = T)

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by Transfer Status (Team: CP)}}}

```{r}
#| label: CrteTrnsfrCP
#| echo: false
#| message: false
#| warning: false
#| paged-print: false
#| tbl-cap: "Unique Interactions by Transfer Status (Team: Carolina Productions)"

  TrnsfrTabCP <- Clean_Event %>% 
  filter(Team== "Carolina Productions") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>% 
  tabyl(Transfer) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(Count)) %>%  
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))

nrow_trnsfr <- nrow(TrnsfrTabCP)
align_vec_trnsfr <- c("l", rep("c", ncol(TrnsfrTabCP) - 1))

kbl(TrnsfrTabCP, booktabs=T, align= align_vec_trnsfr) %>% 
  kable_styling(latex_options = "scale_down", full_width= F) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_trnsfr-1,hline_after = T) %>% 
  row_spec(nrow_trnsfr, bold= T) #%>% 
  #footnote(symbol= footnote1)

```

\newpage
\raggedright\textsf{\textbf{\textit{Unique Interactions by First-Generation Status (Team: CP)}}}

```{r}
#| label: FirstGenCP
#| echo: false
#| message: false
#| warning: false
#| paged-print: false
#| tbl-cap: "Unique Interactions by First-Generation Status (Team: Carolina Productions)"

  CP1stGenTab <- Clean_Event %>% 
  filter(Team== "Carolina Productions") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  rename("FirstGen"= "First-gen") %>% 
  tabyl(FirstGen) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(Count)) %>%  
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))
  

nrow_FrstGenCP <- nrow(CP1stGenTab)
align_vec_FirstGenCP <- c("l", rep("c", ncol(CP1stGenTab) - 1))

kbl(CP1stGenTab, booktabs=T, align= align_vec_FirstGenCP) %>% 
  kable_styling(latex_options = "scale_down", full_width= F) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_FrstGenCP-1,hline_after = T) %>% 
  row_spec(nrow_FrstGenCP, bold= T) #%>% 
  #footnote(symbol= footnote1)

```

### Carolina-Clemson Blood Drive (CCBD)

\raggedright\textsf{\textbf{\textit{Unique Interactions by Race \& Gender (Combined) (Team: CCBD)}}}

```{r}
#| label: RaceGenCCBD
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

GenRaceTabCCBD <- Clean_Event %>% 
  filter(Team=="Carolina Clemson Blood Drive") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  tabyl(Race, Sex) %>% 
  arrange(desc(Female)) %>% 
  adorn_totals(c("row","col")) %>%
  adorn_percentages("all") %>% 
  adorn_pct_formatting(digits = 2) %>% 
  adorn_ns(position = "front")

nrow_CCBD <- nrow(GenRaceTabCCBD)
ncol_CCBD <- ncol(GenRaceTabCCBD)
align_vec_CCBD <- c("l", rep("c", ncol(GenRaceTabCCBD) - 1))

kbl(GenRaceTabCCBD, booktabs = TRUE, caption = "Unique Student Interactions by Race and Gender (Team: Carolina Clemson Blood Drive)", align = align_vec_CCBD) %>%
  kable_styling(latex_options = c("Hold_position", "scale_down")) %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(nrow_CCBD-1, hline_after = TRUE) %>%
  row_spec(nrow_CCBD, bold = TRUE) %>%
  column_spec(ncol_CCBD, bold = TRUE) #%>% 
  #footnote(symbol= footnote1)

GenRaceTabCCBD_cnt <- Clean_Event %>% 
  filter(Team=="Carolina Clemson Blood Drive")
 
nrowUnit_CCBD_written <- scales::comma(nrow(GenRaceTabCCBD_cnt))
nrowUnit_CCBD_numeric <- nrow(GenRaceTabCCBD_cnt)

CCBD_pct <- paste0(format((nrowUnit_CCBD_numeric/nRow_dat * 100), digits=4), "%")

num_duplicate_addressesCCBD <- Clean_Event %>%
  filter(str_detect(Team, "Carolina Clemson Blood Drive")) %>%
  count(`Campus Email`) %>%
  filter(n > 1) %>%
  nrow()

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by College (Team: CCBD)}}}

```{r}
#| label: CollegeTabCCBD
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

CollegeTabCCBD <- Clean_Event %>% 
  filter(Team == "Carolina Clemson Blood Drive") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>% 
  tabyl(College) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(Count)) %>%  
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.))) 
  
nrows_collegeCCBD <- nrow(CollegeTabCCBD)

align_vec_collegeCCBD <- c("l", rep("c", ncol(CollegeTabCCBD) - 1))

kbl(CollegeTabCCBD,booktabs=T, longtable = T, caption= "Unique Student Interactions by College (Team: Carolina Clemson Blood Drive)", align= align_vec_collegeCCBD) %>%
  kable_styling(latex_options = c("hold_position","scale_down"), font_size = 10) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrows_collegeCCBD-1,hline_after = T) %>% 
  row_spec(nrows_collegeCCBD, bold=T) #%>% 
  #footnote(symbol= footnote1)

```

\newpage
\raggedright\textsf{\textbf{\textit{Unique Interactions by Class Standing (Team: CCBD)}}}
```{r}
#| label: ClssStnd_CCBD
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

pacman::p_load("tidyverse", "janitor", "lubridate","stringr","forcats", "openxlsx", "tidyr","kableExtra", "scales", "knitr")

ClssStndTabCCBD <- Clean_Event %>% 
  filter(Team=="Carolina Clemson Blood Drive") %>%
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  tabyl(`Class Standing`) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(`Percentage(%)`)) %>% 
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2)
  

nrow_clssStnd <- nrow(ClssStndTabCCBD)
align_vec_clssstnd <- c("l", rep("c", ncol(ClssStndTabCCBD) - 1))

kbl(ClssStndTabCCBD,booktabs=T, linesep = "", caption= "Unique Student Interactions by Class Standing (Team: Carolina Clemson Blood Drive)", align=align_vec_clssstnd) %>%
  kable_styling(latex_options = c("hold_position","scale_down"), font_size = 10) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_clssStnd-1,hline_after = T) %>% 
  row_spec(nrow_clssStnd, bold=T) #%>% 
  #footnote(symbol= footnote1)

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by Cohort (Unit: CCBD)}}}
```{r}
#| label: ChrtTblCCBD
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

CohortTblCCBD <- Clean_Event %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  filter(Team== "Carolina Clemson Blood Drive", Cohort!= "Missing") %>% 
  tabyl(`Cohort`) %>% 
  rename("Count" = n, "Percentage(%)" = percent) %>%
  arrange(desc(Count)) %>%
  slice_head(n = 6) %>% 
  adorn_totals("row") %>% 
  adorn_pct_formatting(digits = 2) %>% 
  mutate(across(Count, ~ comma(.))) 
   
  
CohortCCBD_missing <- Clean_Event %>% 
  filter(Team== "Carolina Clemson Blood Drive", Cohort== "Unknown") %>% 
  nrow(.) %>% 
  comma(.)
  
nrow_clssStnd <- nrow(CohortTblCCBD)
align_vec_clssstnd <- c("l", rep("c", ncol(CohortTblCCBD) - 1))

kbl(CohortTblCCBD,booktabs=T, linesep="",caption= "Unique Student Interactions by Cohort (Team: Carolina Clemson Blood Drive)", align=align_vec_clssstnd) %>%
  kable_styling(latex_options = c("hold_position","scale_down"), font_size = 10) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_clssStnd-1,hline_after = T) %>% 
  row_spec(nrow_clssStnd, bold=T) %>% 
  footnote(general = "Students with cohort years before AY2019-20 were removed.", threeparttable = T)

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by Transfer Status (Team: CCBD)}}}

```{r}
#| label: CrteTrnsfrCCBD
#| echo: false
#| message: false
#| warning: false
#| paged-print: false
#| tbl-cap: "Unique Interactions by Transfer Status (Team: Carolina Clemson Blood Drive)"

TrnsfrTabCCBD <- Clean_Event %>% 
  filter(Team== "Carolina Clemson Blood Drive") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>% 
  tabyl(Transfer) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(Count)) %>%  
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))

nrow_trnsfr <- nrow(TrnsfrTabCCBD)
align_vec_trnsfr <- c("l", rep("c", ncol(TrnsfrTabCCBD) - 1))

kbl(TrnsfrTabCCBD, booktabs=T, align= align_vec_trnsfr) %>% 
  kable_styling(latex_options = "scale_down", full_width= F) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_trnsfr-1,hline_after = T) %>% 
  row_spec(nrow_trnsfr, bold= T) #%>% 
  #footnote(symbol= footnote1)

```

\newpage
\raggedright\textsf{\textbf{\textit{Unique Interactions by First-Generation Status (Team: CCBD)}}}

```{r}
#| label: FirstGenCCBD
#| echo: false
#| message: false
#| warning: false
#| paged-print: false
#| tbl-cap: "Unique Interactions by First-Generation Status (Team: Carolina Clemson Blood Drive)"

CCBD1stGenTab <- Clean_Event %>% 
  filter(Team== "Carolina Clemson Blood Drive") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  rename("FirstGen"= "First-gen") %>% 
  tabyl(FirstGen) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(Count)) %>%  
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))
  

nrow_FrstGenCCBD <- nrow(CCBD1stGenTab)
align_vec_FirstGenCCBD <- c("l", rep("c", ncol(CCBD1stGenTab) - 1))

kbl(CCBD1stGenTab, booktabs=T, align= align_vec_FirstGenCCBD) %>% 
  kable_styling(latex_options = "scale_down", full_width= F) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_FrstGenCCBD-1,hline_after = T) %>% 
  row_spec(nrow_FrstGenCCBD, bold= T) #%>% 
  #footnote(symbol= footnote1)

```

### Dance Marathon (USCDM)

\raggedright\textsf{\textbf{\textit{Unique Interactions by Race \& Gender (Team: USCDM)}}}

```{r}
#| label: RaceGenUSCDM
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

GenRaceTabUSCDM <- Clean_Event %>%
  filter(Team == "Dance Marathon") %>%
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  tabyl(Race, Sex) %>%
  arrange(desc(Female)) %>%
  adorn_totals(c("row", "col")) %>%
  adorn_percentages("all") %>%
  adorn_pct_formatting(digits = 2) %>%
  adorn_ns(position = "front")

nrow_USCDM <- nrow(GenRaceTabUSCDM)
ncol_USCDM <- ncol(GenRaceTabUSCDM)
align_vec_USCDM <- c("l", rep("c", ncol(GenRaceTabUSCDM) - 1))

GenRaceTabUSCDM <- Clean_Event %>%
  filter(Team == "Dance Marathon") %>%
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  tabyl(Race, Sex) %>%
  arrange(desc(Female)) %>%
  adorn_totals(c("row", "col")) %>%
  adorn_percentages("all") %>%
  adorn_pct_formatting(digits = 2) %>%
  adorn_ns(position = "front")

kbl(GenRaceTabUSCDM, booktabs = TRUE, caption = "Unique Student Interactions by Race and Gender (Team: Dance Marathon)", align = align_vec_USCDM) %>%
  kable_styling(latex_options = c("Hold_position", "scale_down")) %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(nrow_USCDM-1, hline_after = TRUE) %>%
  row_spec(nrow_USCDM, bold = TRUE) %>%
  column_spec(ncol_USCDM, bold = TRUE) #%>% 
  #footnote(symbol= footnote1)

GenRaceTabUSCDM_cnt <- Clean_Event %>% 
  filter(Team=="Dance Marathon")
 
nrowUnit_USCDM_written <- scales::comma(nrow(GenRaceTabUSCDM_cnt))
nrowUnit_USCDM_numeric <- nrow(GenRaceTabUSCDM_cnt)

USCDM_pct <- paste0(format((nrowUnit_USCDM_numeric/nRow_dat * 100), digits=4), "%")

num_duplicate_addressesUSCDM <- Clean_Event %>%
  filter(Team== "Dance Marathon") %>%
  count(`Campus Email`) %>%
  filter(n > 1) %>%
  nrow()

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by College (Team: USCDM)}}}

```{r}
#| label: CollegeTabUSCDM
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

CollegeTabUSCDM <- Clean_Event %>% 
  filter(Team == "Dance Marathon") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>% 
  tabyl(College) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(Count)) %>%  
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))

nrows_collegeUSCDM <- nrow(CollegeTabUSCDM)

align_vec_collegeUSCDM <- c("l", rep("c", ncol(CollegeTabUSCDM) - 1))

kbl(CollegeTabUSCDM,booktabs=T, longtable=T, caption= "Unique Student Interactions by College (Team: Dance Marathon)", align= align_vec_collegeUSCDM) %>%
  kable_styling(latex_options = c("hold_position","scale_down", "repeat_header"), font_size = 10) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrows_collegeUSCDM-1,hline_after = T) %>% 
  row_spec(nrows_collegeUSCDM, bold=T) #%>% 
  #footnote(symbol= footnote1)

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by Class Standing (Team: USCDM)}}}

```{r}
#| label: OvrllClssStnd_USCDM
#| echo: false
#| message: false
#| warning: false
#| paged-print: false


ovrllClssStndTabUSCDM <- Clean_Event %>% 
  filter(Team=="Dance Marathon") %>%
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  tabyl(`Class Standing`) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(`Percentage(%)`)) %>% 
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))

nrow_clssStnd <- nrow(ovrllClssStndTabUSCDM)
align_vec_clssstnd <- c("l", rep("c", ncol(ovrllClssStndTabUSCDM) - 1))

kbl(ovrllClssStndTabUSCDM,booktabs=T, longtable = T,linesep = "", caption= "Unique Student Interactions by Class Standing (Team: Dance Marathon)", align=align_vec_clssstnd) %>%
  kable_styling(latex_options = c("hold_position","scale_down"), font_size = 10) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_clssStnd-1,hline_after = T) %>% 
  row_spec(nrow_clssStnd, bold=T) #%>% 
  #footnote(symbol= footnote1)

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by Cohort (Unit: USCDM)}}}

```{r}
#| label: ChrtTblUSCDM
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

CohortTblUSCDM <- Clean_Event %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  filter(Team== "Dance Marathon",Cohort!= "Missing") %>% 
  tabyl(`Cohort`) %>% 
  rename("Count" = n, "Percentage(%)" = percent) %>%
  arrange(desc(Count)) %>%
  slice_head(n = 6) %>% 
  adorn_totals("row") %>% 
  adorn_pct_formatting(digits = 2) %>% 
  mutate(across(Count, ~ comma(.))) 
   
  
CohortYr_missing <- Clean_Event %>% 
  filter(Team== "Dance Marathon", Cohort== "Unknown") %>% 
  nrow(.) %>% 
  comma(.)
  
nrow_clssStnd <- nrow(CohortTblUSCDM)
align_vec_clssstnd <- c("l", rep("c", ncol(ovrllCohortTbl) - 1))

kbl(CohortTblUSCDM,booktabs=T, linesep="",caption= "Unique Student Interactions by Cohort", align=align_vec_clssstnd) %>%
  kable_styling(latex_options = c("hold_position","scale_down"), font_size = 10) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_clssStnd-1,hline_after = T) %>% 
  row_spec(nrow_clssStnd, bold=T) %>% 
  footnote(general =  "Students with cohort years before AY2020-21 were also removed.", threeparttable= T)

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by Transfer Status (Team: USCDM)}}}

```{r}
#| label: CrteTrnsfrUSCDM
#| echo: false
#| message: false
#| warning: false
#| paged-print: false
#| tbl-cap: "Unique Interactions by Transfer Status (Team: Dance Marathon)"

  TrnsfrTabUSCDM <- Clean_Event %>% 
  filter(Team== "Dance Marathon") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>% 
  tabyl(Transfer) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(Count)) %>%  
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))

nrow_trnsfr <- nrow(TrnsfrTabUSCDM)
align_vec_trnsfr <- c("l", rep("c", ncol(TrnsfrTabUSCDM) - 1))

kbl(TrnsfrTabUSCDM, booktabs=T, align= align_vec_trnsfr) %>% 
  kable_styling(latex_options = "scale_down", full_width= F) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_trnsfr-1,hline_after = T) %>% 
  row_spec(nrow_trnsfr, bold= T) #%>% 
  #footnote(symbol= footnote1)

```

\newpage
\raggedright\textsf{\textbf{\textit{Unique Interactions by First-Generation Status (Team: USCDM)}}}
```{r}
#| label: FirstGenUSCDM
#| echo: false
#| message: false
#| warning: false
#| paged-print: false
#| tbl-cap: "Unique Interactions by First-Generation Status (Team: Dance Marathon)"

  USCDM1stGenTab <- Clean_Event %>% 
  filter(Team== "Dance Marathon") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  rename("FirstGen"= "First-gen") %>% 
  tabyl(FirstGen) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(Count)) %>%  
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))

nrow_FrstGenUSCDM <- nrow(USCDM1stGenTab)
align_vec_FirstGenUSCDM <- c("l", rep("c", ncol(USCDM1stGenTab) - 1))

kbl(USCDM1stGenTab, booktabs=T, align= align_vec_FirstGenUSCDM) %>% 
  kable_styling(latex_options = "scale_down", full_width= F) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_FrstGenUSCDM-1,hline_after = T) %>% 
  row_spec(nrow_FrstGenUSCDM, bold= T) #%>% 
  #footnote(symbol= footnote1)

```

### Gamecock Entertainment (Team)

This section looks at Gamecock Entertainment as a Team. This area covers all signature events, such as Midnight Breakfast and Tiger Burn, as well as other events that do not fit within the other subsections of GE.  

\raggedright\textsf{\textbf{\textit{Unique Interactions by Race \& Gender (Team: GE)}}}

```{r}
#| label: RaceGenTmGE
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

GenRaceTabTmGE <- Clean_Event %>% 
  filter(Team=="Gamecock Entertainment") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  tabyl(Race, Sex) %>% 
  arrange(desc(.)) %>% 
  adorn_totals(c("row","col")) %>%
  adorn_percentages("all") %>% 
  adorn_pct_formatting(digits = 2) %>% 
  adorn_ns(position = "front")

nrow_TmGE <- nrow(GenRaceTabTmGE)
ncol_TmGE <- ncol(GenRaceTabTmGE)
align_vec_TmGE <- c("l", rep("c", ncol(GenRaceTabTmGE) - 1))

kbl(GenRaceTabTmGE, booktabs = TRUE, caption = "Unique Student Interactions by Race and Gender (Team: Gamecock Entertainment)", align = align_vec_TmGE) %>%
  kable_styling(latex_options = c("Hold_position", "scale_down")) %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(nrow_TmGE-1, hline_after = TRUE) %>%
  row_spec(nrow_TmGE, bold = TRUE) %>%
  column_spec(ncol_TmGE, bold = TRUE) #%>% 
  #footnote(symbol= footnote1)

GenRaceTabTmGE_cnt <- Clean_Event %>% 
  filter(Team=="Gamecock Entertainment")
 
nrowUnit_TmGE_written <- scales::comma(nrow(GenRaceTabTmGE_cnt))
nrowUnit_TmGE_numeric <- nrow(GenRaceTabTmGE_cnt)

TmGE_pct <- paste0(format((nrowUnit_TmGE_numeric/nRow_dat * 100), digits=4), "%")

num_duplicate_addressesTmGE <- Clean_Event %>%
  filter(str_detect(Team, "Gamecock Entertainment")) %>%
  count(`Campus Email`) %>%
  filter(n > 1) %>%
  nrow()

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by College (Team: GE)}}}
```{r}
#| label: CollegeTabTmGE
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

CollegeTabTmGE <- Clean_Event %>% 
  filter(Team == "Gamecock Entertainment") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>% 
  tabyl(College) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(Count)) %>%  
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))
  

nrows_collegeTmGE <- nrow(CollegeTabTmGE)

align_vec_collegeTmGE <- c("l", rep("c", ncol(CollegeTabTmGE) - 1))

kbl(CollegeTabTmGE, booktabs=T, longtable=T, caption= "Unique Student Interactions by College (Team: Gamecock Entertainment)", align= align_vec_collegeTmGE) %>%
  kable_styling(latex_options = c("hold_position","scale_down", "repeat_header"), font_size = 10) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrows_collegeTmGE-1,hline_after = T) %>% 
  row_spec(nrows_collegeTmGE, bold=T) #%>% 
  #footnote(symbol= footnote1)

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by Class Standing (Team: GE)}}}
```{r}
#| label: OvrllClssStnd_TmGE
#| echo: false
#| message: false
#| warning: false
#| paged-print: false


ovrllClssStndTabTmGE <- Clean_Event %>% 
  filter(Team=="Gamecock Entertainment") %>%
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  tabyl(`Class Standing`) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(`Percentage(%)`)) %>% 
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))
  

nrow_clssStnd <- nrow(ovrllClssStndTabTmGE)
align_vec_clssstnd <- c("l", rep("c", ncol(ovrllClssStndTabTmGE) - 1))

kbl(ovrllClssStndTabTmGE,booktabs=T, linesep = "", caption= "Unique Student Interactions by Class Standing (Team: Gamecock Entertainment)", align=align_vec_clssstnd) %>%
  kable_styling(latex_options = c("hold_position","scale_down"), font_size = 10) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_clssStnd-1,hline_after = T) %>% 
  row_spec(nrow_clssStnd, bold=T) #%>% 
  #footnote(symbol= footnote1)

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by Cohort (Team: GE)}}}

```{r}
#| label: ChrtTblTmGE
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

CohortTblGE <- Clean_Event %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  filter(Team== "Gamecock Entertainment", Cohort!= "Missing") %>% 
  tabyl(`Cohort`) %>% 
  rename("Count" = n, "Percentage(%)" = percent) %>%
  arrange(desc(Count)) %>%
  slice_head(n = 6) %>% 
  adorn_totals("row") %>% 
  adorn_pct_formatting(digits = 2) %>% 
  mutate(across(Count, ~ comma(.))) 
   
CohortYr_missing <- Clean_Event %>% 
  filter(Team== "Gamecock Entertainment",Cohort== "Missing") %>% 
  nrow(.) %>% 
  comma(.)
  
nrow_clssStnd <- nrow(ovrllCohortTbl)
align_vec_clssstnd <- c("l", rep("c", ncol(ovrllCohortTbl) - 1))

kbl(CohortTblGE,booktabs=T, linesep="",caption= "Unique Student Interactions by Cohort", align=align_vec_clssstnd) %>%
  kable_styling(latex_options = c("hold_position","scale_down"), font_size = 10) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_clssStnd-1,hline_after = T) %>% 
  row_spec(nrow_clssStnd, bold=T) %>% 
  footnote(general = paste0("There are ", CohortYr_missing, " students with missing cohort data. Students with cohort years before AY2020-21 were also removed."), threeparttable=T)

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by Transfer Status (Team: GE)}}}

```{r}
#| label: CrteTrnsfrTmGE
#| echo: false
#| message: false
#| warning: false
#| paged-print: false
#| tbl-cap: "Unique Interactions by Transfer Status (Team: Gamecock Entertainment)"

  TrnsfrTabTmGE <- Clean_Event %>% 
  filter(Team== "Gamecock Entertainment") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>% 
  tabyl(Transfer) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(Count)) %>%  
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))

nrow_trnsfr <- nrow(TrnsfrTabTmGE)
align_vec_trnsfr <- c("l", rep("c", ncol(TrnsfrTabTmGE) - 1))

kbl(TrnsfrTabTmGE, booktabs=T, align= align_vec_trnsfr) %>% 
  kable_styling(latex_options = "scale_down", full_width= F) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_trnsfr-1,hline_after = T) %>% 
  row_spec(nrow_trnsfr, bold= T) #%>% 
  #footnote(symbol= footnote1)

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by First-Generation Status (Team: GE)}}}

```{r}
#| label: FirstGenTmGE
#| echo: false
#| message: false
#| warning: false
#| paged-print: false
#| tbl-cap: "Unique Interactions by First-Generation Status (Team: Gamecock Entertainment)"

  TmGE1stGenTab <- Clean_Event %>% 
  filter(Team== "Gamecock Entertainment") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  rename("FirstGen"= "First-gen") %>% 
  tabyl(FirstGen) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(Count)) %>%  
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))
  

nrow_FrstGenTmGE <- nrow(TmGE1stGenTab)
align_vec_FirstGenTmGE <- c("l", rep("c", ncol(TmGE1stGenTab) - 1))

kbl(TmGE1stGenTab, booktabs=T, align= align_vec_FirstGenTmGE) %>% 
  kable_styling(latex_options = "scale_down", full_width= F) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_FrstGenTmGE-1,hline_after = T) %>% 
  row_spec(nrow_FrstGenTmGE, bold= T) #%>% 
  #footnote(symbol= footnote1)

```

### Live \@ the Underground (LUnd)

\raggedright\textsf{\textbf{\textit{Unique Interactions by Race \& Gender (Team: Live @ the Underground)}}}

```{r}
#| label: RaceGenLiveUnd
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

GenRaceTabLiveUnd <- Clean_Event %>% 
  filter(Team=="Live at the Underground") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  tabyl(Race, Sex) %>% 
  arrange(desc(.)) %>% 
  adorn_totals(c("row","col")) %>%
  adorn_percentages("all") %>% 
  adorn_pct_formatting(digits = 2) %>% 
  adorn_ns(position = "front")

nrow_LiveUnd <- nrow(GenRaceTabLiveUnd)
ncol_LiveUnd <- ncol(GenRaceTabLiveUnd)
align_vec_LiveUnd <- c("l", rep("c", ncol_LiveUnd - 1))

kbl(GenRaceTabLiveUnd, booktabs = TRUE, caption = "Unique Student Interactions by Race and Gender (Team: Live @ the Underground)", align = align_vec_LiveUnd) %>%
  kable_styling(latex_options = c("Hold_position", "scale_down")) %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(nrow_LiveUnd-1, hline_after = TRUE) %>%
  row_spec(nrow_LiveUnd, bold = TRUE) %>%
  column_spec(ncol_LiveUnd, bold = TRUE) #%>% 
  #footnote(symbol= footnote1)

GenRaceTabLiveUnd_cnt <- Clean_Event %>% 
  filter(Team=="Live at the Underground")
 
nrowUnit_LiveUnd_written <- scales::comma(nrow(GenRaceTabLiveUnd_cnt))
nrowUnit_LiveUnd_numeric <- nrow(GenRaceTabLiveUnd_cnt)

LiveUnd_pct <- paste0(format((nrowUnit_LiveUnd_numeric/nRow_dat * 100), digits=4), "%")

num_duplicate_addressesLiveUnd <- Clean_Event %>%
  filter(str_detect(Team, "Live at the Underground")) %>%
  count(`Campus Email`) %>%
  filter(n > 1) %>%
  nrow()

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by College (Team: Live @ the Underground)}}}

```{r}
#| label: CollegeTabLiveUnd
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

CollegeTabLiveUnd <- Clean_Event %>% 
  filter(Team =="Live at the Underground") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>% 
  tabyl(College) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(Count)) %>%  
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))
  

nrows_collegeLiveUnd <- nrow(CollegeTabLiveUnd)
align_vec_collegeLiveUnd <- c("l", rep("c", ncol(CollegeTabLiveUnd) - 1))

kbl(CollegeTabLiveUnd,booktabs=T, longtable=T, caption= "Unique Student Interactions by College (Team: Live @ the Underground)", align= align_vec_collegeLiveUnd) %>%
  kable_styling(latex_options = c("hold_position","scale_down", "repeat_header"), font_size = 10) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrows_collegeLiveUnd-1,hline_after = T) %>% 
  row_spec(nrows_collegeLiveUnd, bold=T) #%>% 
  #footnote(symbol= footnote1)

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by Class Standing (Team: Live @ the Underground)}}}

```{r}
#| label: OvrllClssStnd_LiveUnd
#| echo: false
#| message: false
#| warning: false
#| paged-print: false


ovrllClssStndTabLiveUnd <- Clean_Event %>% 
  filter(Team=="Live at the Underground") %>%
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  tabyl(`Class Standing`) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(`Percentage(%)`)) %>% 
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))
  

nrow_clssStnd <- nrow(ovrllClssStndTabLiveUnd)
align_vec_clssstnd <- c("l", rep("c", ncol(ovrllClssStndTabLiveUnd) - 1))

kbl(ovrllClssStndTabLiveUnd,booktabs=T, linesep = "", caption= "Unique Student Interactions by Class Standing (Team: Live @ the Underground)", align=align_vec_clssstnd) %>%
  kable_styling(latex_options = c("hold_position","scale_down"), font_size = 10) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_clssStnd-1,hline_after = T) %>% 
  row_spec(nrow_clssStnd, bold=T) #%>% 
  #footnote(symbol= footnote1)

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by Cohort (Team:  Live @ the Underground)}}}

```{r}
#| label: ChrtTblLiveUnd
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

CohortTblLiveUnd <- Clean_Event %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  filter(Team== "Live at the Underground", Cohort!= "Missing") %>% 
  tabyl(`Cohort`) %>% 
  rename("Count" = n, "Percentage(%)" = percent) %>%
  arrange(desc(Count)) %>%
  slice_head(n = 6) %>% 
  adorn_totals("row") %>% 
  adorn_pct_formatting(digits = 2) %>% 
  mutate(across(Count, ~ comma(.))) 
   
CohortYr_missing <- Clean_Event %>% 
  filter(Team== "Live at the Underground", Cohort== "Missing") %>% 
  nrow(.) %>% 
  comma(.)
  
nrow_clssStnd <- nrow(ovrllCohortTbl)
align_vec_clssstnd <- c("l", rep("c", ncol(ovrllCohortTbl) - 1))

kbl(CohortTblLiveUnd,booktabs=T, linesep="",caption= "Unique Student Interactions by Cohort", align=align_vec_clssstnd) %>%
  kable_styling(latex_options = c("hold_position","scale_down"), font_size = 10) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_clssStnd-1,hline_after = T) %>% 
  row_spec(nrow_clssStnd, bold=T) %>% 
  footnote(general = paste0("There are ", CohortYr_missing, " students with missing cohort data. Students with cohort years before AY2020-21 were also removed."), threeparttable = T)

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by Transfer Status (Team: Live @ the Underground)}}}

```{r}
#| label: CrteTrnsfrLiveUnd
#| echo: false
#| message: false
#| warning: false
#| paged-print: false
#| tbl-cap: "Unique Interactions by Transfer Status (Team: Live \\@ the Underground)"

  TrnsfrTabLiveUnd <- Clean_Event %>% 
  filter(Team == "Live at the Underground" ) %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>% 
  tabyl(Transfer) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(Count)) %>%  
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))

nrow_trnsfr <- nrow(TrnsfrTabLiveUnd)
align_vec_trnsfr <- c("l", rep("c", ncol(TrnsfrTabLiveUnd) - 1))

kbl(TrnsfrTabLiveUnd, booktabs=T, align= align_vec_trnsfr) %>% 
  kable_styling(latex_options = "scale_down", full_width= F) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_trnsfr-1,hline_after = T) %>% 
  row_spec(nrow_trnsfr, bold= T) #%>% 
  #footnote(symbol= footnote1)

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by First-Generation Status (Team: Live @ the Underground)}}}

```{r}
#| label: FirstGenLiveUnd
#| echo: false
#| message: false
#| warning: false
#| paged-print: false
#| tbl-cap: "Unique Interactions by First-Generation Status (Team: Live \\@ the Underground)"

  LiveUnd1stGenTab <- Clean_Event %>% 
  filter(Team== "Live at the Underground") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  rename("FirstGen"= "First-gen") %>% 
  tabyl(FirstGen) %>% 
  rename("Count"= n, "Percentage(%)"=percent, ) %>%
  arrange(desc(Count)) %>%  
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))
  

nrow_FrstGenLiveUnd <- nrow(LiveUnd1stGenTab)
align_vec_FirstGenLiveUnd <- c("l", rep("c", ncol(LiveUnd1stGenTab) - 1))

kbl(LiveUnd1stGenTab, booktabs=T, align= align_vec_FirstGenLiveUnd) %>% 
  kable_styling(latex_options = "scale_down", full_width= F) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_FrstGenLiveUnd-1,hline_after = T) %>% 
  row_spec(nrow_FrstGenLiveUnd, bold= T) #%>% 
  #footnote(symbol= footnote1)

```

### Thursday After Dark (TAD) 

\raggedright\textsf{\textbf{\textit{Unique Interactions by Race \& Gender (Team: TAD)}}}

```{r}
#| label: RaceGenTAD
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

GenRaceTabTAD <- Clean_Event %>% 
  filter(Team=="Thursday After Dark") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  tabyl(Race, Sex) %>% 
  arrange(desc(.)) %>% 
  adorn_totals(c("row","col")) %>%
  adorn_percentages("all") %>% 
  adorn_pct_formatting(digits = 2) %>% 
  adorn_ns(position = "front")

nrow_TAD <- nrow(GenRaceTabTAD)
ncol_TAD <- ncol(GenRaceTabTAD)
align_vec_TAD <- c("l", rep("c", ncol(GenRaceTabTAD) - 1))

kbl(GenRaceTabTAD, booktabs = TRUE, caption = "Unique Student Interactions by Race and Gender (Team: Thursday After Dark)", align = align_vec_TAD) %>%
  kable_styling(latex_options = c("Hold_position", "scale_down")) %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(nrow_TAD-1, hline_after = TRUE) %>%
  row_spec(nrow_TAD, bold = TRUE) %>%
  column_spec(ncol_TAD, bold = TRUE) #%>% 
  #footnote(symbol= footnote1)

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by College (Team: TAD)}}}

```{r}
#| label: CollegeTabTAD
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

CollegeTabTAD <- Clean_Event %>% 
  filter(Team == "Thursday After Dark") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>% 
  tabyl(College) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(Count)) %>%  
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))

nrows_collegeTAD <- nrow(CollegeTabTAD)
align_vec_collegeTAD <- c("l", rep("c", ncol(CollegeTabTAD) - 1))

kbl(CollegeTabTAD,booktabs=T, longtable=T, caption= "Unique Student Interactions by College (Team: Thursday After Dark)", align= align_vec_collegeTAD) %>%
  kable_styling(latex_options = c("hold_position","scale_down", "repeat_header"), font_size = 10) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrows_collegeTAD-1,hline_after = T) %>% 
  row_spec(nrows_collegeTAD, bold=T) #%>% 
  #footnote(symbol= footnote1)

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by Class Standing (Team: TAD)}}}

```{r}
#| label: ClssStnd_TAD
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

ClssStndTabTAD <- Clean_Event %>% 
  filter(Team=="Thursday After Dark") %>%
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  tabyl(`Class Standing`) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(`Percentage(%)`)) %>% 
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))

nrow_clssStnd <- nrow(ClssStndTabTAD)
align_vec_clssstnd <- c("l", rep("c", ncol(ClssStndTabTAD) - 1))

kbl(ClssStndTabTAD,booktabs=T, longtable = T,linesep = "", caption= "Unique Student Interactions by Class Standing (Team: Thursday After Dark)", align=align_vec_clssstnd) %>%
  kable_styling(latex_options = c("hold_position","scale_down"), font_size = 10) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_clssStnd-1,hline_after = T) %>% 
  row_spec(nrow_clssStnd, bold=T) #%>% 
  #footnote(symbol= footnote1)

```

\newpage
\raggedright\textsf{\textbf{\textit{Unique Interactions by Cohort (Team: TAD)}}}
```{r}
#| label: ChrtTblTAD
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

ChrtTblTAD <-  Clean_Event %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  filter(Team== "Live at the Underground", Cohort!= "Missing") %>% 
  tabyl(`Cohort`) %>% 
  rename("Count" = n, "Percentage(%)" = percent) %>%
  arrange(desc(Count)) %>%
  slice_head(n = 6) %>% 
  adorn_totals("row") %>% 
  adorn_pct_formatting(digits = 2) %>% 
  mutate(across(Count, ~ comma(.))) 
   
CohortYr_missing <- Clean_Event %>% 
  filter(Team== "Live at the Underground", Cohort== "Missing") %>% 
  nrow(.) %>% 
  comma(.)
  
nrow_clssStnd <- nrow(ChrtTblTAD)
align_vec_clssstnd <- c("l", rep("c", ncol(ChrtTblTAD) - 1))

kbl(ChrtTblTAD,booktabs=T, linesep="",caption= "Unique Student Interactions by Cohort", align=align_vec_clssstnd) %>%
  kable_styling(latex_options = c("hold_position","scale_down"), font_size = 10) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_clssStnd-1,hline_after = T) %>% 
  row_spec(nrow_clssStnd, bold=T) %>% 
  footnote(general = paste0("There are ", CohortYr_missing, " students with missing cohort data. Students with cohort years before AY2020-21 were also removed."), threeparttable = T)

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by Transfer Status (Team: TAD)}}}

```{r}
#| label: CrteTrnsfrTAD
#| echo: false
#| message: false
#| warning: false
#| paged-print: false
#| tbl-cap: "Unique Interactions by Transfer Status (Team: Thursday After Dark)"

  TrnsfrTabTAD <- Clean_Event %>% 
  filter(Team== "Thursday After Dark") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>% 
  tabyl(Transfer) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(Count)) %>%  
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))

nrow_trnsfr <- nrow(TrnsfrTabTAD)
align_vec_trnsfr <- c("l", rep("c", ncol(TrnsfrTabTAD) - 1))

kbl(TrnsfrTabTAD, booktabs=T, align= align_vec_trnsfr) %>% 
  kable_styling(latex_options = "scale_down", full_width= F) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_trnsfr-1,hline_after = T) %>% 
  row_spec(nrow_trnsfr, bold= T) #%>% 
  #footnote(symbol= footnote1)

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by First-Generation Status (Team: TAD)}}}

```{r}
#| label: FirstGenTAD
#| echo: false
#| message: false
#| warning: false
#| paged-print: false
#| tbl-cap: "Unique Interactions by First-Generation Status (Team: Thursday After Dark)"

  TAD1stGenTab <- Clean_Event %>% 
  filter(Team== "Thursday After Dark") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  rename("FirstGen"= "First-gen") %>% 
  tabyl(FirstGen) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(Count)) %>%  
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))

nrow_FrstGenTAD <- nrow(TAD1stGenTab)
align_vec_FirstGenTAD <- c("l", rep("c", ncol(TAD1stGenTab) - 1))

kbl(TAD1stGenTab, booktabs=T, align= align_vec_FirstGenTAD) %>% 
  kable_styling(latex_options = "scale_down", full_width= F) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_FrstGenTAD-1,hline_after = T) %>% 
  row_spec(nrow_FrstGenTAD, bold= T) #%>% 
  #footnote(symbol= footnote1)

```

\newpage
### Tuesday Takeover (TT)

\raggedright\textsf{\textbf{\textit{Unique Interactions by Race \& Gender (Team: TT)}}}

```{r}
#| label: RaceGenTT
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

GenRaceTabTT <- Clean_Event %>% 
  filter(Team=="Tuesday Takeover") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  tabyl(Race, Sex) %>% 
  arrange(desc(Female)) %>% 
  adorn_totals(c("row","col")) %>%
  adorn_percentages("all") %>% 
  adorn_pct_formatting(digits = 2) %>% 
  adorn_ns(position = "front")

nrow_TT <- nrow(GenRaceTabTT)
ncol_TT <- ncol(GenRaceTabTT)
align_vec_TT <- c("l", rep("c", ncol(GenRaceTabTT) - 1))

kbl(GenRaceTabTT, booktabs = TRUE, caption = "Unique Student Interactions by Race and Gender (Team: Tuesday Takeover)", align = align_vec_TT) %>%
  kable_styling(latex_options = c("Hold_position", "scale_down")) %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(nrow_TT-1, hline_after = TRUE) %>%
  row_spec(nrow_TT, bold = TRUE) %>%
  column_spec(ncol_TT, bold = TRUE) #%>% 
  #footnote(symbol= footnote1)

GenRaceTabTT_cnt <- Clean_Event %>% 
  filter(Team=="Homecoming")
 
nrowUnit_TT_written <- scales::comma(nrow(GenRaceTabTT_cnt))
nrowUnit_TT_numeric <- nrow(GenRaceTabTT_cnt)

TT_pct <- paste0(format((nrowUnit_TT_numeric/nRow_dat * 100), digits=4), "%")

num_duplicate_addressesTT <- Clean_Event %>%
  filter(str_detect(Team, "Tuesday Takeover")) %>%
  count(`Campus Email`) %>%
  filter(n > 1) %>%
  nrow()

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by College (Team: TT)}}}

```{r}
#| label: CollegeTabTT
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

CollegeTabTT <- Clean_Event %>% 
  filter(Team == "Tuesday Takeover") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>% 
  tabyl(College) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(Count)) %>%  
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))
  

nrows_collegeTT <- nrow(CollegeTabTT)

align_vec_collegeTT <- c("l", rep("c", ncol(CollegeTabTT) - 1))

kbl(CollegeTabTT,booktabs=T, longtable=T, caption= "Unique Student Interactions by College (Team: Tuesday Takeover)", align= align_vec_collegeTT) %>%
  kable_styling(latex_options = c("hold_position","scale_down", "repeat_header"), font_size = 10) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrows_collegeTT-1,hline_after = T) %>% 
  row_spec(nrows_collegeTT, bold=T) #%>% 
  #footnote(symbol= footnote1)

```

\newpage
\raggedright\textsf{\textbf{\textit{Unique Interactions by Class Standing (Team: TT)}}}

```{r}
#| label: OvrllClssStnd_TT
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

ovrllClssStndTabTT <- Clean_Event %>% 
  filter(Team=="Tuesday Takeover") %>%
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  tabyl(`Class Standing`) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(`Percentage(%)`)) %>% 
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))
  

nrow_clssStnd <- nrow(ovrllClssStndTabTT)
align_vec_clssstnd <- c("l", rep("c", ncol(ovrllClssStndTabTT) - 1))

kbl(ovrllClssStndTabTT,booktabs=T, linesep = "", caption= "Unique Student Interactions by Class Standing (Team: Tuesday Takeover)", align=align_vec_clssstnd) %>%
  kable_styling(latex_options = c("hold_position","scale_down"), font_size = 10) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_clssStnd-1,hline_after = T) %>% 
  row_spec(nrow_clssStnd, bold=T) #%>% 
  #footnote(symbol= footnote1)

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by Cohort (Team: TT)}}}

```{r}
#| label: ChrtTblTT
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

CohortTblTT <- Clean_Event %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  filter(Team== "Tuesday Takeover", Cohort!= "Missing") %>% 
  tabyl(`Cohort`) %>% 
  rename("Count" = n, "Percentage(%)" = percent) %>%
  arrange(desc(Count)) %>%
  slice_head(n = 6) %>% 
  adorn_totals("row") %>% 
  adorn_pct_formatting(digits = 2) %>% 
  mutate(across(Count, ~ comma(.))) 
   
CohortYr_missing <- Clean_Event %>% 
  filter(Team== "Tuesday Takeover", Cohort== "Missing") %>% 
  nrow(.) %>% 
  comma(.)
  
nrow_clssStnd <- nrow(CohortTblTT)
align_vec_clssstnd <- c("l", rep("c", ncol(CohortTblTT) - 1))

kbl(CohortTblTT,booktabs=T, linesep="",caption= "Unique Student Interactions by Cohort", align=align_vec_clssstnd) %>%
  kable_styling(latex_options = c("hold_position","scale_down"), font_size = 10) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_clssStnd-1,hline_after = T) %>% 
  row_spec(nrow_clssStnd, bold=T) %>% 
  footnote(general = paste0("There are ", CohortYr_missing, " students with missing cohort data. Students with cohort years before AY2020-21 were also removed."), threeparttable = T)

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by Transfer Status (Team: Tuesday Takeover)}}}

```{r}
#| label: CrteTrnsfrTT
#| echo: false
#| message: false
#| warning: false
#| paged-print: false
#| tbl-cap: "Unique Interactions by Transfer Status (Team\\: Tuesday Takeover)"

  TrnsfrTabTT <- Clean_Event %>% 
  filter(Team== "Tuesday Takeover") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>% 
  tabyl(Transfer) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(Count)) %>%  
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))

nrow_trnsfr <- nrow(TrnsfrTabTT)
align_vec_trnsfr <- c("l", rep("c", ncol(TrnsfrTabTT) - 1))

kbl(TrnsfrTabTT, booktabs=T, align= align_vec_trnsfr) %>% 
  kable_styling(latex_options = "scale_down", full_width= F) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_trnsfr-1,hline_after = T) %>% 
  row_spec(nrow_trnsfr, bold= T) #%>% 
  #footnote(symbol= footnote1)

```

\newpage
\textsf{\textbf{\textit{Unique Interactions by First-Generation Status (Team: Tuesday Takeover)}}}

```{r}
#| label: FirstGenTT
#| echo: false
#| message: false
#| warning: false
#| paged-print: false
#| tbl-cap: "Unique Interactions by First-Generation Status (Team\\: Tuesday Takeover)"

  TT1stGenTab <- Clean_Event %>% 
  filter(Team== "Tuesday Takeover") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  rename("FirstGen"= "First-gen") %>% 
  tabyl(FirstGen) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(Count)) %>%  
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))
  

nrow_FrstGenTT <- nrow(TT1stGenTab)
align_vec_FirstGenTT <- c("l", rep("c", ncol(TT1stGenTab) - 1))

kbl(TT1stGenTab, booktabs=T, align= align_vec_FirstGenTT) %>% 
  kable_styling(latex_options = "scale_down", full_width= F) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_FrstGenTT-1,hline_after = T) %>% 
  row_spec(nrow_FrstGenTT, bold= T) #%>% 
  #footnote(symbol= footnote1)

```

## Leadership and Service Center (LSC)

\raggedright\textsf{\textbf{\textit{Unique Interactions by Race \& Gender (Combined) (Unit: LSC)}}}

```{r}
#| label: RaceGenLSC
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

GenRaceTabLSC <- Clean_Event %>% 
  filter(Unit=="LSC") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  tabyl(Race, Sex) %>% 
  arrange(desc(Female)) %>% 
  adorn_totals(c("row","col")) %>%
  adorn_percentages("all") %>% 
  adorn_pct_formatting(digits = 2) %>% 
  adorn_ns(position = "front")

nrow_LSC <- nrow(GenRaceTabLSC)
ncol_LSC <- ncol(GenRaceTabLSC)
align_vec_LSC <- c("l", rep("c", ncol(GenRaceTabLSC) - 1))

kbl(GenRaceTabLSC, booktabs = TRUE, caption = "Unique Student Interactions by Race and Gender", align = align_vec_LSC) %>%
  kable_styling(latex_options = c("Hold_position", "scale_down")) %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(nrow_LSC-1, hline_after = TRUE) %>%
  row_spec(nrow_LSC, bold = TRUE) %>%
  column_spec(ncol_LSC, bold = TRUE) #%>% 
  #footnote(symbol= footnote1)

GenRaceTabLSC_cnt <- Clean_Event %>% 
  filter(Unit=="LSC")
 
nrowUnit_LSC_written <- scales::comma(nrow(GenRaceTabLSC_cnt))
nrowUnit_LSC_numeric <- nrow(GenRaceTabLSC_cnt)

LSC_pct <- paste0(format((nrowUnit_LSC_numeric/nRow_dat * 100), digits=4), "%")

totalEvents_UnitTeams <- unique(Clean_Event[,c("Unit", "Team", "Event")]) %>% 
  group_by(Unit, Team) %>% 
  summarize(Count= n(), .groups = "drop") %>% 
  arrange()

TotalEvents_Unit <- unique(Clean_Event[,c("Unit", "Team", "Event")]) %>% 
  group_by(Unit) %>% 
  summarize(Count=n())

numLSC_events <- TotalEvents_Unit %>% 
  dplyr::filter(Unit== "LSC") %>% 
  dplyr::pull(Count)
```

The Leadership and Service Center as a whole accounted for `{r} nrowUnit_LSC_written` total student interactions making up `{r} LSC_pct` of the total student engagements, hosting `{r} numLSC_events` events. These tables show theat the majority of attendees are White Females. 

\raggedright\textsf{\textbf{\textit{Unique Interactions by College (Unit: LSC)}}}

```{r}
#| label: CollegeTabLSC
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

CollegeTabLSC <- Clean_Event %>% 
  filter(Unit == "LSC") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>% 
  tabyl(College) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(Count)) %>%  
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))
  
nrows_collegeLSC <- nrow(CollegeTabLSC)

align_vec_collegeLSC <- c("l", rep("c", ncol(CollegeTabLSC) - 1))

kbl(CollegeTabLSC,booktabs=T, longtable= T, caption= "Unique Student Interactions by College", align= align_vec_collegeGE) %>%
  kable_styling(latex_options = c("hold_position","scale_down"), font_size = 10) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrows_collegeLSC-1,hline_after = T) %>% 
  row_spec(nrows_collegeLSC, bold=T) #%>% 
  #footnote(symbol= footnote1)

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by Class Standing (Unit: LSC)}}}

```{r}
#| label: OvrllClssStndLSC
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

pacman::p_load("tidyverse", "janitor", "lubridate","stringr","forcats", "openxlsx", "tidyr","kableExtra", "scales", "knitr")

ovrllClssStndTabLSC <- Clean_Event %>% 
  filter(Unit=="LSC") %>%
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  tabyl(`Class Standing`) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(`Percentage(%)`)) %>% 
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.))) 
  
nrow_clssStnd <- nrow(ovrllClssStndTabLSC)
align_vec_clssstnd <- c("l", rep("c", ncol(ovrllClssStndTabLSC) - 1))

kbl(ovrllClssStndTabLSC,booktabs=T, linesep = "", caption= "Unique Student Interactions by Class Standing", align=align_vec_clssstnd) %>%
  kable_styling(latex_options = c("hold_position","scale_down"), font_size = 10) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_clssStnd-1,hline_after = T) %>% 
  row_spec(nrow_clssStnd, bold=T) #%>% 
  #footnote(symbol= footnote1)
```

\textsf{\textbf{\textit{Unique Interactions by Cohort (Team: LSC)}}}
```{r}
#| label: ChrtTblLSC
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

CohortTblLSC <- Clean_Event %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  filter(Unit== "LSC", Cohort!= "Missing") %>% 
  tabyl(`Cohort`) %>% 
  rename("Count" = n, "Percentage(%)" = percent) %>%
  arrange(desc(Count)) %>%
  slice_head(n = 6) %>% 
  adorn_totals("row") %>% 
  adorn_pct_formatting(digits = 2) %>% 
  mutate(across(Count, ~ comma(.))) 
   
CohortYr_missing <- Clean_Event %>% 
  filter(Unit== "LSC", Cohort== "Missing") %>% 
  nrow(.) %>% 
  comma(.)
  
nrow_clssStnd <- nrow(CohortTblLSC)
align_vec_clssstnd <- c("l", rep("c", ncol(CohortTblLSC) - 1))

kbl(CohortTblLSC,booktabs=T, linesep="",caption= "Unique Student Interactions by Cohort", align=align_vec_clssstnd) %>%
  kable_styling(latex_options = c("hold_position","scale_down"), font_size = 10) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_clssStnd-1,hline_after = T) %>% 
  row_spec(nrow_clssStnd, bold=T) %>% 
  footnote(general = paste0("There are ", CohortYr_missing, " students with missing cohort data. Students with cohort years before AY2020-21 were also removed."), threeparttable = T)

```

\newpage
\raggedright\textsf{\textbf{\textit{Unique Interactions by Transfer Status (Unit: LSC)}}}
```{r}
#| label: CrteTrnsfrLSC
#| echo: false
#| message: false
#| warning: false
#| paged-print: false
#| tbl-cap: "Unique Interactions by Transfer Status"

  TrnsfrTabLSC <- Clean_Event %>% 
  filter(Unit== "LSC") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>% 
  tabyl(Transfer) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(Count)) %>%  
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))

nrow_trnsfr <- nrow(TrnsfrTabLSC)
align_vec_trnsfr <- c("l", rep("c", ncol(TrnsfrTabLSC) - 1))

kbl(TrnsfrTabLSC, booktabs=T, align= align_vec_trnsfr) %>% 
  kable_styling(latex_options = "scale_down", full_width= F) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_trnsfr-1,hline_after = T) %>% 
  row_spec(nrow_trnsfr, bold= T) #%>% 
  #footnote(symbol= footnote1)

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by First-Generation Status (Unit: LSC)}}}

```{r}
#| label: FirstGenLSC
#| echo: false
#| message: false
#| warning: false
#| paged-print: false
#| tbl-cap: "Unique Interactions by First-Generation Status"

  LSC1stGenTab <- Clean_Event %>% 
  filter(Unit== "LSC") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  rename("FirstGen"= "First-gen") %>% 
  tabyl(FirstGen) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(Count)) %>%  
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))

nrow_FrstGen <- nrow(LSC1stGenTab)
align_vec_trnsfer <- c("l", rep("c", ncol(LSC1stGenTab) - 1))

kbl(LSC1stGenTab, booktabs=T, align= align_vec_trnsfer) %>% 
  kable_styling(latex_options = "scale_down", full_width= F) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_FrstGen-1,hline_after = T) %>% 
  row_spec(nrow_FrstGen, bold= T) #%>% 
  #footnote(symbol= footnote1)

```

## Center for Student Engagement (CSE)

\raggedright\textsf{\textbf{\textit{Unique Interactions by Race \& Gender (Combined) (Unit: CSE)}}}

```{r}
#| label: RaceGenCSE
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

GenRaceTabCSE <- Clean_Event %>% 
  filter(Unit=="CSE") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  tabyl(Race, Sex) %>% 
  arrange(desc(Female)) %>% 
  adorn_totals(c("row","col")) %>%
  adorn_percentages("all") %>% 
  adorn_pct_formatting(digits = 2) %>% 
  adorn_ns(position = "front")

nrow_CSE <- nrow(GenRaceTabCSE)
ncol_CSE <- ncol(GenRaceTabCSE)
align_vec_CSE <- c("l", rep("c", ncol(GenRaceTabCSE) - 1))

kbl(GenRaceTabCSE, booktabs = TRUE, caption = "Unique Student Interactions by Race and Gender", align = align_vec_CSE) %>%
  kable_styling(latex_options = c("Hold_position", "scale_down")) %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(nrow_CSE-1, hline_after = TRUE) %>%
  row_spec(nrow_CSE, bold = TRUE) %>%
  column_spec(ncol_CSE, bold = TRUE) #%>% 
  #footnote(symbol= footnote1)

GenRaceTabCSE_cnt <- Clean_Event %>% 
  filter(Unit=="CSE")
 
nrowUnit_CSE_written <- scales::comma(nrow(GenRaceTabCSE_cnt))
nrowUnit_CSE_numeric <- nrow(GenRaceTabCSE_cnt)

CSE_pct <- paste0(format((nrowUnit_CSE_numeric/nRow_dat * 100), digits=4), "%")

totalEvents_UnitTeams <- unique(Clean_Event[,c("Unit", "Team", "Event")]) %>% 
  group_by(Unit, Team) %>% 
  summarize(Count= n(), .groups = "drop") %>% 
  arrange()

TotalEvents_Unit <- unique(Clean_Event[,c("Unit", "Team", "Event")]) %>% 
  group_by(Unit) %>% 
  summarize(Count=n())

numCSE_events <- TotalEvents_Unit %>% 
  dplyr::filter(Unit== "CSE") %>% 
  dplyr::pull(Count)
```

The Leadership and Service Center as a whole accounted for `{r} nrowUnit_CSE_written` total student interactions making up `{r} CSE_pct` of the total student engagements, hosting `{r} numLSC_events` events. These tables show theat the majority of attendees are Balck Females. 

\newpage
\raggedright\textsf{\textbf{\textit{Unique Interactions by College (Unit: CSE)}}}

```{r}
#| label: CollegeTabCSE
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

CollegeTabCSE <- Clean_Event %>% 
  filter(Unit == "CSE") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>% 
  tabyl(College) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(Count)) %>%  
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))
  
nrows_collegeCSE <- nrow(CollegeTabCSE)
align_vec_collegeCSE <- c("l", rep("c", ncol(CollegeTabCSE) - 1))

kbl(CollegeTabCSE, booktabs=T, longtable = T, caption= "Unique Student Interactions by College", align= align_vec_collegeCSE) %>%
  kable_styling(latex_options = c("hold_position","scale_down"), font_size = 10) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrows_collegeCSE-1,hline_after = T) %>% 
  row_spec(nrows_collegeCSE, bold=T) #%>% 
  #footnote(symbol= footnote1)

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by Class Standing (Unit: CSE)}}}

```{r}
#| label: OvrllClssStndCSE
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

pacman::p_load("tidyverse", "janitor", "lubridate","stringr","forcats", "openxlsx", "tidyr","kableExtra", "scales", "knitr")

ovrllClssStndTabCSE <- Clean_Event %>% 
  filter(Unit=="CSE") %>%
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  tabyl(`Class Standing`) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(`Percentage(%)`)) %>% 
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.))) 
  
nrow_clssStnd <- nrow(ovrllClssStndTabCSE)
align_vec_clssstnd <- c("l", rep("c", ncol(ovrllClssStndTabCSE) - 1))

kbl(ovrllClssStndTabCSE,booktabs=T, linesep = "", caption= "Unique Student Interactions by Class Standing", align=align_vec_clssstnd) %>%
  kable_styling(latex_options = c("hold_position","scale_down"), font_size = 10) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_clssStnd-1,hline_after = T) %>% 
  row_spec(nrow_clssStnd, bold=T) #%>% 
  #footnote(symbol= footnote1)
```

\newpage
\textsf{\textbf{\textit{Unique Interactions by Cohort (Team: CSE)}}}

```{r}
#| label: ChrtTblCSE
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

CohortTblCSE <- Clean_Event %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  filter(Unit== "CSE", Cohort!= "Missing") %>% 
  tabyl(`Cohort`) %>% 
  rename("Count" = n, "Percentage(%)" = percent) %>%
  arrange(desc(Count)) %>%
  slice_head(n = 6) %>% 
  adorn_totals("row") %>% 
  adorn_pct_formatting(digits = 2) %>% 
  mutate(across(Count, ~ comma(.))) 
   
CohortYr_missing <- Clean_Event %>% 
  filter(Unit== "CSE", Cohort== "Missing") %>% 
  nrow(.) %>% 
  comma(.)
  
nrow_clssStnd <- nrow(ovrllCohortTbl)
align_vec_clssstnd <- c("l", rep("c", ncol(ovrllCohortTbl) - 1))

kbl(CohortTblCSE,booktabs=T, linesep="",caption= "Unique Student Interactions by Cohort", align=align_vec_clssstnd) %>%
  kable_styling(latex_options = c("hold_position","scale_down"), font_size = 10) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_clssStnd-1,hline_after = T) %>% 
  row_spec(nrow_clssStnd, bold=T) %>% 
  footnote(general = paste0("There are ", CohortYr_missing, " students with missing cohort data. Students with cohort years before AY2020-21 were also removed."), threeparttable = T)

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by Transfer Status (Unit: CSE)}}}
```{r}
#| label: CrteTrnsfrCSE
#| echo: false
#| message: false
#| warning: false
#| paged-print: false
#| tbl-cap: Unique Interactions by Transfer Status

  TrnsfrTabCSE <- Clean_Event %>% 
  filter(Unit== "CSE") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>% 
  tabyl(Transfer) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(Count)) %>%  
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))

nrow_trnsfr <- nrow(TrnsfrTabCSE)
align_vec_trnsfr <- c("l", rep("c", ncol(TrnsfrTabCSE) - 1))

kbl(TrnsfrTabCSE, booktabs=T, align= align_vec_trnsfr) %>% 
  kable_styling(latex_options = "scale_down", full_width= F) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_trnsfr-1,hline_after = T) %>% 
  row_spec(nrow_trnsfr, bold= T) #%>% 
  #footnote(symbol= footnote1)

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by First-Generation Status (Unit: CSE)}}}

```{r}
#| label: FirstGenCSE
#| echo: false
#| message: false
#| warning: false
#| paged-print: false
#| tbl-cap: "Unique Interactions by First-Generation Status"

  CSE1stGenTab <- Clean_Event %>% 
  filter(Unit== "RHUU") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  rename("FirstGen"= "First-gen") %>% 
  tabyl(FirstGen) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(Count)) %>%  
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))

nrow_FrstGen <- nrow(CSE1stGenTab)
align_vec_trnsfer <- c("l", rep("c", ncol(CSE1stGenTab) - 1))

kbl(CSE1stGenTab, booktabs=T, align= align_vec_trnsfer) %>% 
  kable_styling(latex_options = "scale_down", full_width= F) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_FrstGen-1,hline_after = T) %>% 
  row_spec(nrow_FrstGen, bold= T) #%>% 
  #footnote(symbol= footnote1)

```

\newpage
## Student Governance (StuGov)

\raggedright\textsf{\textbf{\textit{Unique Interactions by Race \& Gender (Combined) (Unit: StuGov)}}}

```{r}
#| label: RaceGenStuGov
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

GenRaceTabSG <- Clean_Event %>% 
  filter(Unit=="SG") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  tabyl(Race, Sex) %>% 
  arrange(desc(Female)) %>% 
  adorn_totals(c("row","col")) %>%
  adorn_percentages("all") %>% 
  adorn_pct_formatting(digits = 2) %>% 
  adorn_ns(position = "front")

nrow_SG <- nrow(GenRaceTabSG)
ncol_SG <- ncol(GenRaceTabSG)
align_vec_SG <- c("l", rep("c", ncol(GenRaceTabSG) - 1))

kbl(GenRaceTabSG, booktabs = TRUE, caption = "Unique Student Interactions by Race and Gender", align = align_vec_SG) %>%
  kable_styling(latex_options = c("Hold_position", "scale_down")) %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(nrow_SG-1, hline_after = TRUE) %>%
  row_spec(nrow_SG, bold = TRUE) %>%
  column_spec(ncol_SG, bold = TRUE) #%>% 
  #footnote(symbol= footnote1)

GenRaceTabSG_cnt <- Clean_Event %>% 
  filter(Unit=="SG")
 
nrowUnit_SG_written <- scales::comma(nrow(GenRaceTabSG_cnt))
nrowUnit_SG_numeric <- nrow(GenRaceTabSG_cnt)

SG_pct <- paste0(format((nrowUnit_SG_numeric/nRow_dat * 100), digits=4), "%")

totalEvents_UnitTeams <- unique(Clean_Event[,c("Unit", "Team", "Event")]) %>% 
  group_by(Unit, Team) %>% 
  summarize(Count= n(), .groups = "drop") %>% 
  arrange()

TotalEvents_Unit <- unique(Clean_Event[,c("Unit", "Team", "Event")]) %>% 
  group_by(Unit) %>% 
  summarize(Count=n())

numSG_events <- TotalEvents_Unit %>% 
  dplyr::filter(Unit== "SG") %>% 
  dplyr::pull(Count)
```

The Leadership and Service Center as a whole accounted for `{r} nrowUnit_SG_written` total student interactions making up `{r} SG_pct` of the total student engagements, hosting `{r} numLSC_events` events. These tables show theat the majority of attendees are White Females. 

\raggedright\textsf{\textbf{\textit{Unique Interactions by College (Unit: SG)}}}

```{r}
#| label: CollegeTabSG
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

CollegeTabSG <- Clean_Event %>% 
  filter(Unit == "SG") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>% 
  tabyl(College) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(Count)) %>%  
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))
  
nrows_collegeSG <- nrow(CollegeTabSG)
align_vec_collegeSG <- c("l", rep("c", ncol(CollegeTabSG) - 1))

kbl(CollegeTabSG, booktabs=T, longtable = T, caption= "Unique Student Interactions by College", align= align_vec_collegeSG) %>%
  kable_styling(latex_options = c("hold_position","scale_down"), font_size = 10) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrows_collegeSG-1,hline_after = T) %>% 
  row_spec(nrows_collegeSG, bold=T) #%>% 
  #footnote(symbol= footnote1)

```

\newpage
\raggedright\textsf{\textbf{\textit{Unique Interactions by Class Standing (Unit: SG)}}}

```{r}
#| label: OvrllClssStndSG
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

pacman::p_load("tidyverse", "janitor", "lubridate","stringr","forcats", "openxlsx", "tidyr","kableExtra", "scales", "knitr")

ovrllClssStndTabSG <- Clean_Event %>% 
  filter(Unit=="SG") %>%
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  tabyl(`Class Standing`) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(`Percentage(%)`)) %>% 
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.))) 
  
nrow_clssStnd <- nrow(ovrllClssStndTabSG)
align_vec_clssstnd <- c("l", rep("c", ncol(ovrllClssStndTabSG) - 1))

kbl(ovrllClssStndTabSG,booktabs=T, linesep = "", caption= "Unique Student Interactions by Class Standing", align=align_vec_clssstnd) %>%
  kable_styling(latex_options = c("hold_position","scale_down"), font_size = 10) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_clssStnd-1,hline_after = T) %>% 
  row_spec(nrow_clssStnd, bold=T) #%>% 
  #footnote(symbol= footnote1)
```

\textsf{\textbf{\textit{Unique Interactions by Cohort (Team: SG)}}}

```{r}
#| label: ChrtTblSG
#| echo: false
#| message: false
#| warning: false
#| paged-print: false

CohortTblSG <- Clean_Event %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  filter(Unit== "SG", Cohort!= "Missing") %>% 
  tabyl(`Cohort`) %>% 
  rename("Count" = n, "Percentage(%)" = percent) %>%
  arrange(desc(Count)) %>%
  slice_head(n = 6) %>% 
  adorn_totals("row") %>% 
  adorn_pct_formatting(digits = 2) %>% 
  mutate(across(Count, ~ comma(.))) 
   
CohortYr_missing <- Clean_Event %>% 
  filter(Unit== "SG", Cohort== "Missing") %>% 
  nrow(.) %>% 
  comma(.)
  
nrow_clssStnd <- nrow(ovrllCohortTbl)
align_vec_clssstnd <- c("l", rep("c", ncol(ovrllCohortTbl) - 1))

kbl(CohortTblTT,booktabs=T, linesep="",caption= "Unique Student Interactions by Cohort", align=align_vec_clssstnd) %>%
  kable_styling(latex_options = c("hold_position","scale_down"), font_size = 10) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_clssStnd-1,hline_after = T) %>% 
  row_spec(nrow_clssStnd, bold=T) %>% 
  footnote(general = paste0("There are ", CohortYr_missing, " students with missing cohort data. Students with cohort years before AY2020-21 were also removed."), threeparttable = T)

```

\raggedright\textsf{\textbf{\textit{Unique Interactions by Transfer \& First-Generation Students Status (Unit: SG)}}}
```{r}
#| label: CrteTrnsfrSG
#| echo: false
#| message: false
#| warning: false
#| paged-print: false
#| tbl-cap: Unique Interactions by Transfer Status

  TrnsfrTabSG <- Clean_Event %>% 
  filter(Unit== "SG") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>% 
  tabyl(Transfer) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(Count)) %>%  
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))

nrow_trnsfr <- nrow(TrnsfrTabSG)
align_vec_trnsfr <- c("l", rep("c", ncol(TrnsfrTabSG) - 1))

kbl(TrnsfrTabSG, booktabs=T, align= align_vec_trnsfr) %>% 
  kable_styling(latex_options = "scale_down", full_width= F) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_trnsfr-1,hline_after = T) %>% 
  row_spec(nrow_trnsfr, bold= T) #%>% 
  #footnote(symbol= footnote1)

```

```{r}
#| label: FirstGenSG
#| echo: false
#| message: false
#| warning: false
#| paged-print: false
#| tbl-cap: "Unique Interactions by First-Generation Status"

  SG1stGenTab <- Clean_Event %>% 
  filter(Unit== "SG") %>% 
  distinct(`Campus Email`, .keep_all = TRUE) %>%
  rename("FirstGen"= "First-gen") %>% 
  tabyl(FirstGen) %>% 
  rename("Count"= n, "Percentage(%)"=percent) %>%
  arrange(desc(Count)) %>%  
  adorn_totals("row") %>% 
  adorn_pct_formatting(,digits=2) %>% 
  mutate(across(Count, ~comma(.)))

nrow_FrstGen <- nrow(SG1stGenTab)
align_vec_trnsfer <- c("l", rep("c", ncol(SG1stGenTab) - 1))

kbl(SG1stGenTab, booktabs=T, align= align_vec_trnsfer) %>% 
  kable_styling(latex_options = "scale_down", full_width= F) %>% 
  row_spec(0, bold=T) %>% 
  row_spec(nrow_FrstGen-1,hline_after = T) %>% 
  row_spec(nrow_FrstGen, bold= T) #%>% 
  #footnote(symbol= footnote1)

```




